Self Regulation Ontology Retest Analyses

### 2019-01-23 code/SRO_Retest_Analyses.Rmd
more figure work

```{r}
rel_comp %>%
  group_by(dv, task) %>%
  summarise(mean_lit = mean(retest_reliability),
            mean_emp = unique(mean_pearson)) %>%
  ggplot(aes(mean_emp, mean_lit, col=task, shape=task))+
  geom_smooth(method="lm")+
  geom_point()+
  xlim(-0.25, 1)+
  ylim(-0.25, 1)+
  ylab("Average Literature Reliability Estimate")+
  xlab("Average Empirical Reliability Estimate")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
  labs(caption = str_wrap("FIGURE 2: Correlation between mean reliability estimates for each measure found in the literature with the mean reliability from our data.", width = 120))
```

>>>>

```{r}
rel_comp %>%
  group_by(dv, task) %>%
  summarise(mean_lit = mean(retest_reliability),
            mean_emp = unique(mean_pearson)) %>%
  ggplot(aes(mean_emp, mean_lit, col=task, shape=task))+
  geom_smooth(method="lm")+
  geom_point()+
  xlim(-0.25, 1)+
  ylim(-0.25, 1)+
  ylab("Average Literature Reliability Estimate")+
  xlab("Average Empirical Reliability Estimate")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))
```
